\cvsection{Experience}
\begin{cventries}
\cventry{
	    MACS-CIB
    }
    {Sr Lead Software Engineer | Macro eTrading Rates Derivatives | MACS | Vice President }
    {JP Morgan|Singapore}
    {Dec. 2018 - Current}
    {
      \begin{cvitems}
        \item {Software Engineering Manager for Margin and Collateral APAC development}
        \item {Built multiple features for Rates Derivatives Product on OMS using FIX protocol and AMPS data bus}
        \item {Integrated auto-quoting feature for RFM/RFQ for rates product for Bloomberg, TradeWeb venues}
        \item {Enhanced RDM to manage interest rate swap market data from external venues such as Bloomberg, TradeWeb}
        \item {Built margin calculation investigation portal with ticket matching and un-structured data reconciliation (using DAG).}
        \item {Enriched multiple applications (using ELK/Grafana/Jaeger) with technology stack of Spring Boot, React, Kafka, ElasticSearch and Apache Cassandra.}
      \end{cvitems}
    }
\cventry{
	    Reference Data-GMOT
    }
    {APAC Reference Data Engineering Manager | Scala Developer | Semantic Data Model | Vice President}
    {Bank of America|Singapore}
    {Jul. 2014 - Dec. 2018}
    {
      \begin{cvitems}
        \item {Software Engineering Manager for APAC client reference data application development team}
        \item {Develop application, scripts and data pipelines to process structured data near real-time}
        \item {Developed Spark rules on Cloudera Hadoop distribution for Data Quality Checks.}
        \item {Built Business process workflow for Japanese fund on-boarding applications.}
        \item {Built parser for bpm workflow DSL using PEG.js and natural language processor to deduce duplicate entities using Apache Lucene.}
      \end{cvitems}
    }
\cventry{
	    Luxor Developer-GMOT
    }
    {Java Developer | InMemory Data Grid}
    {ANZ|Singapore}
    {Sep. 2012 - Jul. 2014}
    {
      \begin{cvitems}
        \item {Built TradeRepository for OTC trades  supports Rates, FX, and Commodities using Gemfire NoSQL InMemory Data Grid.}
        \item {Monte-Carlo simulation engine accesses data using 1000 core HPC grid.}
        \item {Developed an automated testing framework to replay 1000s of combinations of OTC Trade lifecycle.}
        \item {Built reconciliation for backward binary compatibility and regression-testing.}
      \end{cvitems}
    }
  \cventry
    {SABRE IntraDay Risk Platform}
    {Risk Software Engineer | Mu/Haskell Quant Tools}
    {Standard Chartered Bank|Singapore}
    {May. 2011 - Sep. 2012}
    {
      \begin{cvitems}
        \item {Developed End-of-Day reconciliation system for MUREX flow trades using embedded database.}
        \item {Server side javascript development, stream MXML as Trade Data Repository objects.}
        \item {Mu-Script/Haskell development that calculates risk for Interest rate product.}
        \item {Developed JUnit tests for Rates and FX derivatives pricing engine.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {Investment-Bank Developer | Java/Spring Framework}
    {Credit Suisse|Singapore}
    {Apr. 2007 - May. 2011}
    {
      \begin{cvitems}
        \item {Built many applications using Java and Spring Framework.}
        \item {Acted as APAC Java Application Platform Architect.}
        \item {Built code analyzing graph tool to find duplicate components.}
        \item {IT Solution Architect for Private Bank applications.}
        \item {Lead a team of java developers to build applications for Private Bank.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {Investment-Bank Developer | Java/Spring Framework}
    {Standard Chartered Bank|India}
    {Dec. 2004 - Apr. 2007}
    {
      \begin{cvitems}
        \item {Built applications using Java and Struts Framework.}
      \end{cvitems}
    }
  \cventry
    {Senior Software Engineer}
    {Developer | Java/Visual-Basic}
    {Aspire Systems|India}
    {Oct. 2002 - Dec. 2004}
    {
      \begin{cvitems}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {Developer | Visual-Basic}
    {Bharatplant Consulting Ltd|India}
    {Feb. 2000 - Oct. 2002}
    {
      \begin{cvitems}
      \end{cvitems}
    }
\end{cventries}
